\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-04-28 chapters/1_intro.tex
Update algorithm description
Start rewriting related work

\emph{Instance segmentation} is a task of computer vision consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
The most success in instance segmentation (IS) has been achieved by applying deep learning \cite{he2017mask,romera2016recurrent,liu2018affinity}. There are two main types of successful deep learning approaches to IS: proposal-based and proposal-free methods. Proposal-based methods consist of two steps: object detection, for example by finding bounding boxes, and assigning pixels to the detected objects \cite{he2017mask,dai2016instance,li2017fully}. Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes. 
% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
Proposal-free methods perform IS by directly predicting pixel features and then using a clustering algorithm for grouping pixels into object instances \TODO{REFS}. In this work, we focus on a proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance. Recently, \cite{liu2018affinity} used this approach and achieved performances comparable to proposal-based methods on the Cityscapes dataset; \UPDATE{similarly, the method was used in \cite{wolf2018mutex} to achieve state-of-the-art results in a neuron segmentation challenge.}

@@

A popular method for graph clustering is hierarchical clustering (HC) which creates an hierarchy of clusters. Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}. This method requires the user to choose a level in the cluster hierarchy defining the desired output clustering.

@@

Finally, \UPDATE{we test these different agglomerative clustering algorithms} on the task of instance segmentation both on the CREMI neuron segmentation challenge and the Cityscapes dataset, by comparing achieved scores, efficiency and robustness to noisy edge weights.

\TODO{Add chapters description}

>>>>

\emph{Instance segmentation} is a task of computer vision consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
The most success in instance segmentation (IS) has been achieved by applying deep learning \cite{he2017mask,romera2016recurrent,liu2018affinity}. There are two main types of successful deep learning approaches to IS: proposal-based and proposal-free methods. Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances \cite{he2017mask,dai2016instance,li2017fully}. Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes. 
% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting pixel features and then grouping pixels into object instances \TODO{REFS}. In this work, we focus on a proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance. Recently, \cite{liu2018affinity} used this approach and achieved performances comparable to proposal-based methods on the Cityscapes dataset; \UPDATE{similarly, the method was used in \cite{wolf2018mutex} to achieve state-of-the-art results in a neuron segmentation challenge.} \TODO{Rewrite}

@@

Another popular method for graph clustering is hierarchical clustering (HC) which creates an hierarchy of clusters. Agglomerative HC is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}. This method requires the user to choose a level in the cluster hierarchy defining the desired output clustering.

@@

Finally, \UPDATE{we test these different agglomerative clustering algorithms} on the task of instance segmentation both on the CREMI neuron segmentation challenge and the Cityscapes dataset, by comparing achieved scores, efficiency and robustness to noisy edge weights. \TODO{Add chapters description}

### 2019-04-28 chapters/2_rel_work.tex
Update algorithm description
Add descr. of experimental setup
Start rewriting related work

\section{Related work}
\begin{itemize}
\item \textbf{Proposal based methods} 
\begin{itemize}
\item Generate region proposals or bounding boxes and classify the objects in the bounding box \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}; fully convolutional  box proposals \cite{li2017fully}. 
\item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
\item these somehow still uses some kind of object detector (at least to find the number of objects), but they do not necessary analyse one proposal at the time: use an object detector to enumerate candidate instances and then perform pixel-level segmentation of each instance \cite{liang2018proposal,dai2016instance,li2017fully,liang2016reversible,arnab2017pixelwise} \TODO{check \cite{dai2016instance}}
% \SOURCE{\cite{kong2018recurrent}
\end{itemize}

\item \textbf{Proposal-free methods:} 
\begin{itemize}
\item box-free \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask}; joint segmentation and instance labeling in a combinatorial framework \cite{kirillov2017instancecut}; recurrent models \cite{romera2016recurrent,ren2017end}; encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; sequential framework to gradually group from points to lines and then instances \cite{liu2017sgn}
% \item From end-to-end recurrent attention: \textit{Other approaches us- ing FCNs are proposal-free, but rely on a \textbf{bottom-up merging process}\textbf{}. Liang et al. [26] predict dense pixel prediction of ob- ject location and size, using clustering as a post-processing step. Uhrig et al. [41] present another approach based on FCNs, which is trained to produces a semantic segmen- tation as well as an instance-aware angle map, encoding the instance centroids. Post-processing based on template matching and instance fusion produces the instance identi- ties. Importantly, they also used ground-truth depth labels in training. Concurrent work [2, 19, 22] also explores a similar idea of using FCNs to output instance-sensitive embeddings.}
\item \textbf{Pixel embedding vectors}: 
\begin{itemize}
\item supervised vectors \cite{bai2017deep}, unsupervised vectors  \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic} of which \cite{kong2018recurrent} is trained end-to-end;  using scene depth information \cite{uhrig2016pixel}, \TODO{check \cite{sironi2014multiscale}} 
%    \TODO{more on pose estimation, vector distance transform, deep coloring?, ECCV semi-convolutions}

% different types of loss
% \item For each pixel in the image, a CNN predicts an embedding vector, such that pixels in the same instance are represented by the same vector. (\textit{by training a model that labels pixels with unit-length vectors that live in some ﬁxed dimension embedding space} \SOURCE{Rec. embeddings} ). \textit{With instance embedding, each object is assigned a “color” in a n-dimensional space. The network processes the image and produces a dense output, same size as the input image. Each pixel in the output of the network is a point in the embedding space. Pixels that belong to the same object are close in the embedding space while pixels that belong to different objects are distant in the embedding space. Parsing the image embedding space involves some sort of clustering algorithm.} \SOURCE{online}

% \item Clustering methods: DBSCAN, more

\item \emph{Division by used clustering methods}: spectral clustering \cite{liang2018proposal}; mean-shift \cite{kong2018recurrent}; HDBSCAN \cite{}; seeds \cite{fathi2017semantic} \TODO{incomplete}
\end{itemize}

% \item Nevertheless, in both approaches we can define a grid graph (each vertex representing a pixel) with signed weights and find the final instance segmentation by using a graph partitioning algorithm:
% \begin{itemize}
% \item In Method 1, the graph is complete and the edge weights represent similarities between pairs of pixel embedding vectors. In most proposed approaches, embedding vectors representing distinct instances should be "distant enough" in the embedding space (a minimum distance is usually used during the training of the CNN). Thus, this threshold distance can be used to define signed affinities, representing attraction or repulsion between pairs of pixels;
% \item  In Method 2, the short- and long-range affinities predicted by the CNN are directly used as signed edge weights in the grid graph
% \end{itemize}

\item \textbf{Most related: predict short- and long-range affinities}. For each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors) and CNN predicts how likely it is for each pixel pair to be in the same instance \cite{liu2018affinity,wolf2018mutex,lee2017superhuman,xie2015holistically,Maire_2016_CVPR}. Mention that  \cite{liu2018affinity} is SoA on cityscapes for proposal-free methods and \cite{wolf2018mutex} is SoA on ISBI
% \item \cite{liu2018affinity} achieved comparable results to methods based on object proposal like Mask-R-CNN on natural images (Cityscapes); \cite{wolf2018mutex} achieved SOA results on a biological images (ISBI)
% \item Side comment: Even with pixel embedding vectors we can deduce affinities or signed costs
% (see MWS paper for a good review)

@@

\item hierarchy and multicut proposals \cite{funke2018candidate}
\item \textit{Must-not-link edges:} initially introduced as hard-constraints \cite{malmberg2011generalized}, then introduced dynamically \cite{wolf2018mutex,levinkov2017comparative}. 
\item Local-search approximations of MC: greeedy fixation and greedy additive edge contraction \cite{levinkov2017comparative}
\end{itemize}
\end{itemize}

>>>>

\section{Related work} \label{sec:related_work}

% \begin{itemize}
% \item Motivation 2:
% \begin{itemize}
% \item HC has been always really popular in computer vision: \emph{Instance segmentation} is a task of computer vision that involves the detection of all objects in an image by performing pixel-level segmentation of each instance.   
% \item Since conventional unsigned graph agglomerative clustering algorithms, such as the well-known linkage methods [1], usually are quite sensitive to noise and outliers [1] (As their affinities are directly computed using pairwise distances between samples), most methods were based on multi-step pipelines first predicting superpixels (to reduce noise).
% \item These methods are still commonly used for specific instance segmentation applications: connectomics, build merge-tree 
%  %https://arxiv.org/pdf/1208.5092.pdf
% \item still commonly used for building merge-trees, give recent examples in connectomics (Sebastian Seung, etc...) % https://arxiv.org/abs/1608.04051
% \item Graph clustering algorithms recently gained more and more popularity with the advent of deep-learning and its application to instance segmentation
% \item Deep convolutional neural nets (CNNs) has been successfully applied to a wide range of tasks of computer vision and pixel-level image understanding, such as \UPDATE{boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, semantic segmentation \cite{long2015fully,chen2018deeplab,kong2018recurrent}, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet}, and pose estimation \cite{wei2016convolutional,cao2017realtime}.}
% % \SOURCE{\cite{kong2018recurrent}}

% \item Currently there are two successful approaches used for proposal-free bottom-up instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}

% \item Both approaches requires a final clustering algorithm to output the final instance segmentation

%  and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections

%  and find the final instance segmentation by using a graph clustering algorithm.

% \item GMIS achieved 
% comparable results to methods based on object 
% proposal like Mask-R-CNN on natural images 
% (Cityscapes); MWS achieved SOA results on a 
% biological images (ISBI)

% \item Out contributions:

% \begin{itemize}
%  \item we compare different types of agglomeration clustering on a pixel grid graph with short and long-range connections, focusing on aspects like efficieny, robustness (and quality of the final clustering in terms of multicut energy) \textbf{Comparison paper}
%  \item \textit{if we get good scores on CREMI dataset}: we show that also on neuro-data it is worth to skip the hand-crafted superpixel step and compute the final segmentation directly from the CNN affinities (MWS already showed it on the ISBI dataset): main selling point is again the almost-parameter free feature of the method
% \end{itemize}
% \end{itemize}
% \end{itemize}

% More details about instance segmentation (move to related work)
% \begin{itemize}

% \item 
% \item Many recent successful methods for instance segmentation %, usually named \emph{proposal-based methods}, 
%  use heuristic approaches that start from the classical computer vision task of \emph{object detection}, where the goal is to localize each objects using a bounding box, and then predict both a pixel-level mask of each instance and a semantic label (classify the objects in the bounding box). \TODO{Is it really general enough as a description...?} \cite{yang2012layered,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible,he2017mask}
% \item While effective, these approaches are \UPDATE{somewhat unsatisfying (copy/paste, change: present some faults)} because:
% \begin{itemize}
% \item they rely on the object detector and non-maximum suppression heuristics to count how many instances are present in the image, 
% \item they tend to underperform in cluttered scenes, since instance assignment is often carried out independently for each detection; 
% \item they are not usable for wiry or articulated objects (e.g. in the field of connectomics and neuron segmenation from electron microscopy images) 
% \item their architecture do not usually prevent a pixel to be shared between multiple instances
% \item they do not scale up well since each proposal has to be singularly processed by the CNN. 
% % \item (difficult to train in an end-to-end manner: interface between instance segmentation and detection is non-differentiable)
% % \item (architecture is complex and hard to tune and “debug”...?)
% \end{itemize}

% \item Currently there are two successful approaches used for proposal-free (make brief intro) instance segmentation: the first ones predict associative pixel embedding vectors, where the goal is to have a CNN predicting embedding vectors that are similar only for pixels in the same instance \cite{kong2018recurrent,fathi2017semantic,newell2017associative,de2017semantic}; in the second type of approaches, for every pixel a set of neighboring pixels is fixed  (not necesarelly limited to the direct neighbors) and a CNN then predicts affinities, that represent how likely it is for each of neighboring pixels to be in the same instance \cite{liu2018affinity,wolf2018mutex,xie2015holistically}

% \item Both approaches requires a final clustering algorithm to output the final instance segmentation

%  and we can define a grid graph, where each vertex represents a pixel, with short- and long-range edge connections

%  and find the final instance segmentation by using a graph clustering algorithm.

% \item Recent work (\cite{wolf2018mutex}, more...) shows that it is better to use \textbf{repulsion and attraction} (directly predict it with the classifier, no need to define seeds or to fix a threshold given an hierarchy of clusters)
% \item solving correlation clustering problem (multicut) is too expensive for this application (even using recently proposed heuristics)
% \item our contributions:
% \begin{itemize}
% \item we propose a unified and simple formalization of Agglomerative Clustering and show how many of the recently proposed methods can be seen as special cases (focusing in particular on signed graphs) (\textbf{review and comparison paper})
% \item new clustering algorithms on signed graphs

% \end{itemize}
% \item on other datasets (connectomics) many methods are based on multi-step pipelines first predicting superpixels

% \end{itemize}

% \item Motivation 1:

% \begin{itemize}

% \item all HC methods only talk about positive edge weights, but it is actually easy to generalize them for negative and attractive edges. 
% \item The standard version of HC is good for building hierarchy but problem with hierarchical merge-trees is how to choose one single threshold. Choose one single fixed density level. Ideally we would like to be able to cut the tree at different places to select our clusters.
% \item An important line of research is based on the observation that superior partitionings are obtained when the graph has both attractive and repulsive edges. Solutions that optimally balance attraction and repulsion do not require external stopping criteria such as predefined number of regions or seeds. This generalization leads to the NP-hard problem of correlation clustering or (synonymous) multicut (MC) partitioning. \emph{Alternative:} multicut / correlation clustering partitions vertices with both attractive and repulsive interactions encoded into the edges of a graph. Multicut has the great advantage that a “natural” partitioning of a graph can be found, without needing to specify a desired number of clusters, or a termination criterion, or one seed per region. Its great drawback is that its optimization is NP-hard.

% \end{itemize}
In recent years there has been considerable progress in pixel-level understanding tasks of computer vision, such as semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
and pose estimation \cite{wei2016convolutional,cao2017realtime}. This progress was mostly associated with new key ideas and architectures of deep convolutional convolutional networks (CNNs), like dilated/``atrous'' convolutions \cite{yu2015multi,chen2018deeplab} or ``hourglass'' architectures with skip connections \cite{ronneberger2015u,paszke2016enet} increasing the receptive field of view of the model.

\textbf{Proposal-based instance segmentation methods} decompose the segmentation task into two steps that consists in generating object proposals or bounding boxes and assigning to each object a class and a binary segmentation mask \cite{he2017mask,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}. 
% Here I could have more: \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask} and probably something more in Deep coloring
% \item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
They commonly rely on Faster RCNN \cite{ren2015faster} and can be trained end-to-end using non-maximum suppression. Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.

\textbf{Proposal-free methods} avoid the limitations of box proposals (e.g. for wiry objects) by directly grouping pixels into instances. For example, some approaches use a combinatorial framework for joint segmentation \cite{kirillov2017instancecut}, whereas others sequentially group pixels into lines and then instances \cite{liu2017sgn}.
% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
A watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction and a template matching scheme using scene depth information is proposed in \cite{uhrig2016pixel}.
Another line of research uses metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,novotny2018semi,kulikov2018instance} 
% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
A clustering algorithm, e.g. HDBSCAN, is then applied to retrieve instances: for example, a model was trained end-to-end in \cite{kong2018recurrent} by using a mean-shift algorithm.
%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

\textbf{Boundary prediction} is another task that has seen noticeable progress thanks to deep supervision \cite{xie2015holistically,kokkinos2015pushing}. 
Our work is based on \cite{liu2018affinity}, where a model is trained to classify whether a pair of pixels (not necessarily given by direct neighbors) belong to the same instance.

\begin{itemize}
    \item Ciao
\begin{itemize}
\item \textbf{Most related: predict short- and long-range affinities}. For each pixel we fix a set of neighboring pixels (not necessarily limited to the direct neighbors) and CNN predicts how likely it is for each pixel pair to be in the same instance \cite{liu2018affinity,wolf2018mutex,lee2017superhuman,xie2015holistically,Maire_2016_CVPR}. Mention that  \cite{liu2018affinity} is SoA on cityscapes for proposal-free methods and \cite{wolf2018mutex} is SoA on ISBI
% \item \cite{liu2018affinity} achieved comparable results to methods based on object proposal like Mask-R-CNN on natural images (Cityscapes); \cite{wolf2018mutex} achieved SOA results on a biological images (ISBI)
% \item Side comment: Even with pixel embedding vectors we can deduce affinities or signed costs
% (see MWS paper for a good review)

@@

\item hierarchy and multicut proposals \cite{funke2018candidate}
\item \textit{Must-not-link edges:} initially introduced as hard-constraints \cite{malmberg2011generalized}, then introduced dynamically \cite{wolf2018mutex,levinkov2017comparative}. 
\item Local-search approximations of MC: greeedy fixation and greedy additive edge contraction \cite{levinkov2017comparative}, and mention size-depending GAEC
\end{itemize}
\item Section 4 requires to related work in connectomics!
\item Conclusion: we specifically build on top of work by......!! We combine the work of MWS, GMIS, GAEC, GF by defining a simple framework and then compare them!
\end{itemize}

### 2019-04-28 chapters/3_algorithm.tex
Start rewriting related work

An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph. Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$. Edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 

@@

\paragraph{The proposed edge contraction algorithm} The proposed generalized Algorithm \ref{main_alg} then proceeds as follows, similarly to the one proposed in \cite{levinkov2017comparative}. It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first. It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}$, does the following: in case of attractive interaction $\tilde{\cost}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig. \ref{fig:edge_contraction_and_contr_graph}. 

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative HC by returning only one single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}). The choice of update rule determines the type of linkage (Table \ref{tab:linkage-criteria}, column 2, unsigned graphs).

On the other hand, in the case of graphs with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative} (Table \ref{tab:linkage-criteria}, sum update rule, row 1). They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.

A clustering algorithm for signed graphs dynamically introducing cannot-link constraints was also proposed in \cite{wolf2018mutex}. In the supplementary material (Sec. \ref{sec:equivalence_MWS}) we show how this algorithm, named Mutex Watershed, can be seen as an efficient implementation of \algname{} with the \emph{absolute-maximum} update rule defined in Table \ref{tab:linkage-criteria}, row 2. Then, we also observe that, for this choice of update rule, \algname{} returns the same clustering with or without cannot-link constraints.

New variations of agglomerative clustering on signed graphs that, to our knowledge, were never mentioned in the literature are given by \algname{} with update rules \emph{mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}).

In this work we test and compare the five update rules listed in Table \ref{tab:linkage-criteria} that represents the most common options. 
Apart from these, \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features. Other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}), whereas 
\cite{funke2018large} uses a \emph{quantile} update rule by populating a histogram for each inter-cluster interaction.

>>>>

An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph. Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$ including $u\in V$. Edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 

@@

\paragraph{The proposed edge contraction algorithm} Algorithm \ref{main_alg} then proceeds as follows, similarly to the one presented in \cite{levinkov2017comparative}. It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first. It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}$, does the following: in case of attractive interaction $\tilde{\cost}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig. \ref{fig:edge_contraction_and_contr_graph}. 

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative HC by returning only one single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}), where the choice of update rule determines the type of linkage (Table \ref{tab:linkage-criteria}, column 2 with unsigned graphs).

Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was already proposed in \cite{levinkov2017comparative} (Table \ref{tab:linkage-criteria}, sum update rule, row 1). They present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms solving the multicut optimization problem.

Another proposed clustering algorithm for signed graphs, named Mutex Watershed \cite{wolf2018mutex}, also introduces dynamical cannot-link constraints. In the supplementary material (Sec. \ref{sec:equivalence_MWS}) we show how it can be seen as an efficient implementation of \algname{} with the \emph{absolute-maximum} update rule defined in Table \ref{tab:linkage-criteria} and we also observe that this case the algorithm returns the same clustering with or without enforcing cannot-link constraints.

On the other hand, new variations of agglomerative clustering on signed graphs that, to our knowledge, were never mentioned in the literature are given by \algname{} with update rules \emph{mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}).

In this work we test and compare these algorithms and the five update rules listed in Table \ref{tab:linkage-criteria} that represent the most common options. 
Nevertheless, more elaborated options exist: \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}), whereas 
\cite{funke2018large} uses a \emph{quantile} update rule by populating a histogram for each inter-cluster interaction.

### 2019-04-28 chapters/5_experiments_noise.tex
Start rewriting related work

    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge}. (a) shows the original predictions $F(x)$, (b) the merge-biased version $\tilde{F}_{+}(x;\mathcal{K})$ defined in Eq. \ref{eq:noise_biased_predictions} and c) the split-biased version $\tilde{F}_{-}(x;\mathcal{K})$. Blue pixels represent boundary evidence.
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
    \end{minipage}\hspace{0.04\textwidth}
\begin{minipage}{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.341 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of update rules.  }
    \label{tab:results_cityscapes}
\end{minipage}
\end{minipage}

>>>>

    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). 
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
    \end{minipage}\hspace{0.04\textwidth}
\begin{minipage}{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.341 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of update rules.  }
    \label{tab:results_cityscapes}
\end{minipage}
\end{minipage}
